### 2022-03-01 doc/contrastive-learning.tex
adds results for contrastive 2D-3D experiment results

@@

>>>>

                CME - Full, Contrast                            & 0.899          & 0.960          & 0.820          & 0              & 0.369          & 0.527          & 0.584          & 0.757          & 0.849          & 0.551          & 0.713          & 0.697          & 0.529          & 0.635          \\

@@

\subsubsection{01.03.2022 - Image to 3D full pretraining}

\textbf{Details:} Using the 2D Features learned from the previous experiment with a 2D pre-training objective, the goal was to transfer these 2D features over to the 3D points. This formed one side of the loss function, while the other side came from a 3D contrastive loss which compared points in the two transformed scans.

\textbf{Results:} The results seem to show an improvement over baseline, and slightly over previous attempts. So far the best effort from 2D transfer learning. But still much bellow PointGroup.
